Response to the defense feedback

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

\textbf{Our Solution}
We abandoned IR and expended the effort to implement
symbolic execution directly on x86 instructions.
Table~\ref{scala:ir} shows that eliminating the IR reduces the number
of instructions examined during analysis. Previous works~\cite{217563} also
adopted a similar approach to speed up fuzzing. Our implementation differs
from that work in two aspects: 1) We use complete constraints. 2) We run the
symbolic execution on one execution path each time. Our approach is approximately 30 times faster than using an IR (transferring ISA into IR and
symbolically executing it).

@@

The tool runs symbolic execution on top of execution traces. At the beginning of the symbolic execution, the tool creates new symbols for each byte in the raw buffer. For other data in the register or memory at the beginning, we use actual values from the runtime execution information. During the symbolic execution for each instruction, the tool updates every variable in the memory and registers with a math formula. The formula is made up of concrete values and symbols accumulated through the symbolic execution. We implement several rules to simplify the formulas. For each formula, the tool will check whether it can be reduced into a concrete values (e.g., $k_1+12-k_1 = 12$ ). If so, the tool will only use the concrete values in the following symbolic execution.

>>>>

\textbf{Our Solution}
We abandoned IR layers and expended the effort to implement
symbolic execution directly on x86 instructions.
Table~\ref{scala:ir} shows that eliminating the IR reduces the number
of instructions examined during analysis. Previous works~\cite{217563} also
adopted a similar approach to speed up fuzzing. Our implementation differs
from that work in two aspects: 1) We use complete constraints. 2) We run the
symbolic execution on one execution path each time. Our approach is approximately 30 times faster than using an IR (transferring ISA into IR and
symbolically executing it).

@@

The tool runs symbolic execution on top of execution traces. At the beginning of the symbolic execution, the tool creates new symbols for each byte in the raw buffer. For other data in the register or memory at the beginning, we use concrete values from the runtime execution information. During the symbolic execution for each instruction, the tool updates every variable in the memory and registers with a math formula. The formula is made up of concrete values and symbols accumulated through the symbolic execution. We implement several rules to simplify the formulas. For each formula, the tool will check whether it can be reduced into a concrete values (e.g., $k_1+12-k_1 = 12$ ). If so, the tool will only use the concrete values in the following symbolic execution.
